[Re] Marriage and happiness: Oishi, Kesebir, and Diener (2011)

### 2020-02-10 analysis/paper.Rmd
adding the RMD file with bibliography

---
title: "Replication Project"
author: "Lauren Heintz, Ben Brodeur Mathieu, Will Wright and Tara Wilson"
date: "February 9, 2020"
output: bookdown::word_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "[Re] Marriage and happiness: Oishi, Kesebir, and Diener (2011)"
author: "Lauren Heintz, Tara Wilson, Ben Mathieu, Will Wright"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: bookdown::word_document2
bibliography: bibliography.bibtex
link-citations: yes

---

``` {r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures")
#knitr::read_chunk("src/my-external-code.R")
```

# Introduction

# Methods

# Results

# Conclusion

# References

Reference 1: @marriagehappiness  
Reference 2: @data

---
